Efficient Coalition Formation for Web Services

### 2013-03-11 papers/coalition/coalition.tex
Changes

%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment. If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone. 
$w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter. Note that $ \sum_{m}{w_m} = 1 $. In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion. We use the same merge-and-split algorithm like ``Web Services and Many Communities'' scenario, to find stable coalitions of web serivces.

@@

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.

@@

As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our data set and form random coalitions consisting of 3 to 25 web services. We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core. We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1. The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.

>>>>

%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment. If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone. 
$w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter. Note that $ \sum_{m}{w_m} = 1 $. In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion. Here, we utilized the same merge-and-split algorithm which we applied for the \emph{``Web Services and Many Communities''} scenario, to find stable coalitions of web serivces.

@@

Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$ which would made that impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.

@@

As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our data set and formed around 10,000 random coalitions consisting of 3 to 25 web services. We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$}-core. We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1. The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$}-core solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.
